Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support)

### 2017-02-14 csf-2017/paper.tex
A shorter version of the stack management discipline paragraph

\begin{figure}
  \begin{align*}
    \addr   &\in& \Addrs &\isdef \nats\\
    w &\in&\Words &\isdef \ints + \Caps \\
    \perm   &\in& \Perms &::= \noperm \mid \readonly\mid \readwrite\mid \readwritel\mid \exec\mid \entry\mid \rwx\mid \rwlx\\
    \gl&\in&\Globals & ::= \glob \mid \local \\
     && \Caps  &::= \left\{
                       \begin{multlined}
                         ((\perm,\gl),\start,\addrend,\addr)\mid\\
                         \start\in\Addrs,\addrend \in
                         \Addrs\cup \{\infty\}
                       \end{multlined} \right\}\\
    r       &\in& \RegName&\bnfdef \pcreg\mid r_0\mid r_1\mid\ldots\\
    \reg &\in& \Regs  &\isdef \RegName \rightarrow \Words\\
    m&\in& \Heaps &\isdef \Addrs \rightarrow \Words \\
    \Phi    &\in& \ExecConfs  &\isdef \Regs \times \Heaps \\
    &&\Confs &::= \ExecConfs + \{\failed \} + \{\halted\} \times \Heaps \\
    \ms     &\in& \MemSegments &::= \Addrs \parfun \Words
  \end{align*}
  \begin{equation*}
  \begin{array}{rcl}
    \rv    &\in& \ints + \RegName \\
    i      &::=& 
                 \jmp{\lv} \mid 
                 \jnz{\lv}{\rv} \mid
                 \move{\lv}{\rv} \mid 
                 \load{\lv}{\hv} \mid 
                 \store{\hv}{\rv} \mid  \\
           &   & \plus{\lv}{\rv}{\rv} \mid 
                 \minus{\lv}{\rv}{\rv} \mid 
                 \lea{\lv}{\rv} \mid 
                 \restricttwo{\lv}{\rv} \mid \\
           &   & \subseg{\lv}{\rv}{\rv} \mid  
                 \isptr{\lv}{\rv} \mid 
                 \getp{\lv}{\lv} \mid 
                 \getl{\lv}{\lv} \mid\\ 
           &   & \getb{\lv}{\lv} \mid
                 \gete{\lv}{\lv} \mid
                 \geta{\lv}{\lv} \mid 
                 \fail \mid
                 \halt 
  \end{array}
\end{equation*}
  \caption{The syntax of our capability machine assembly language.}
  \label{fig:syntax}
\end{figure}

@@

\textbf{Stack management discipline}
The precautions the stack discipline must take have now been introduced and motivated. Summarized, the stack discipline is:
\begin{description}
\item[At program startup] a local $\rwlx$-capability (the stack pointer) resides in register $r_\stk$. The system does not hand out global write-local capabilities.
\item[Before returning to the adversary] clear the registers (with words we do not want to pass to the adversary) and erase any part of the stack we have used.
\item[Before invoking the adversary] push an activation record to the stack, create a local $\entry$-capability for the restore instructions of the activation record (the return pointer) and leave it in register $r_0$, leave a copy of the stack capability restricted to the unused part in $r_\stk$, erase the part of the stack we release control over, and clear the non-argument registers.
\item[Before invoking an adversary call] make sure it is a global capability.
\item[When having a call back invoked by the adversary] make sure the alleged stack pointer has permission $\rwlx$.
\end{description}

@@

\section{Examples}
\label{sec:examples}
In this section, we demonstrate how our formal model of capability
safety allows us to prove local state encapsulation and control-flow
integrity properties for challenging program examples. The security
measures of Section~\ref{sec:stack-and-return-pointer} are deployed to
ensure these properties. Since we are dealing with assembly language,
there are many details to the formal treatment, and therefore we
necessarily have to omit some details in the lemmas we state here.
The interested reader can find all the technical details in the
techincal appendix~\cite{XXX}.

>>>>

\begin{figure}
  \begin{align*}
    \addr   &\in& \Addrs &\isdef \nats\\
    w &\in&\Words &\isdef \ints + \Caps \\
    \perm   &\in& \Perms &::= \noperm \mid \readonly\mid \readwrite\mid \readwritel\mid \exec\mid \entry\mid \rwx\mid \rwlx\\
    \gl&\in&\Globals & ::= \glob \mid \local \\
     && \Caps  &::= \left\{
                       \begin{multlined}
                         ((\perm,\gl),\start,\addrend,\addr)\mid\\
                         \start,\addr\in\Addrs,\addrend \in
                         \Addrs\cup \{\infty\}
                       \end{multlined} \right\}\\
    r       &\in& \RegName&\bnfdef \pcreg\mid r_0\mid r_1\mid\ldots\\
    \reg &\in& \Regs  &\isdef \RegName \rightarrow \Words\\
    m&\in& \Heaps &\isdef \Addrs \rightarrow \Words \\
    \Phi    &\in& \ExecConfs  &\isdef \Regs \times \Heaps \\
    &&\Confs &::= \ExecConfs + \{\failed \} + \{\halted\} \times \Heaps \\
    \ms     &\in& \MemSegments &::= \Addrs \parfun \Words
  \end{align*}
  \begin{equation*}
  \begin{array}{rcl}
    \rv    &\in& \ints + \RegName \\
    i      &::=& 
                 \jmp{\lv} \mid 
                 \jnz{\lv}{\rv} \mid
                 \move{\lv}{\rv} \mid 
                 \load{\lv}{\hv} \mid 
                 \store{\hv}{\rv} \mid  \\
           &   & \plus{\lv}{\rv}{\rv} \mid 
                 \minus{\lv}{\rv}{\rv} \mid 
                 \lea{\lv}{\rv} \mid 
                 \restricttwo{\lv}{\rv} \mid \\
           &   & \subseg{\lv}{\rv}{\rv} \mid  
                 \isptr{\lv}{\rv} \mid 
                 \getp{\lv}{\lv} \mid 
                 \getl{\lv}{\lv} \mid\\ 
           &   & \getb{\lv}{\lv} \mid
                 \gete{\lv}{\lv} \mid
                 \geta{\lv}{\lv} \mid 
                 \fail \mid
                 \halt 
  \end{array}
\end{equation*}
  \caption{The syntax of our capability machine assembly language.}
  \label{fig:syntax}
\end{figure}

@@

\textbf{Stack management discipline}
The precautions the stack discipline must take have now been introduced and motivated. Summarized, the stack discipline is:
\emph{At program startup} a local $\rwlx$-capability (the stack pointer) resides in register $r_\stk$. The system does not hand out global write-local capabilities.
\emph{Before returning to the adversary} clear the registers (with words we do not want to pass to the adversary) and erase any part of the stack we have used.
\emph{Before invoking the adversary} push an activation record to the stack, create a local $\entry$-capability for the restore instructions of the activation record (the return pointer) and leave it in register $r_0$, leave a copy of the stack capability restricted to the unused part in $r_\stk$, erase the part of the stack we release control over, and clear the non-argument registers.
\emph{Before invoking an adversary call} make sure it is a global capability.
\emph{When having a call back invoked by the adversary} make sure the alleged stack pointer has permission $\rwlx$.

@@

\section{Examples}
\label{sec:examples}
In this section, we demonstrate how our formal model of capability
safety allows us to prove local state encapsulation and control-flow
integrity properties for challenging program examples. The security
measures of Section~\ref{sec:stack-and-return-pointer} are deployed to
ensure these properties. Since we are dealing with assembly language,
there are many details to the formal treatment, and therefore we
necessarily have to omit some details in the lemmas we state here.
The interested reader can find all the technical details in the
technical appendix~\cite{XXX}.
